Learning and Evaluation of \strips\ Action Models with Classical Planning

### 2018-05-23 doc/aij18/learning_task.tex

In this paper we address the $\Lambda=\tup{\mathcal{M},\Psi,\mathcal{T}}$ learning task with the following assumptions:
\begin{enumerate}
\item Each input action scheme $\xi\in\mathcal{M}$ is at least composed of its $head(\xi)$,
\item The initial state $s_0\in\mathcal{T}$ is {\em fully observable}.
\item Intermediate actions $a_i\in\mathcal{T}$ and states $s_i\in\mathcal{T}$ s.t. {\small $1\leq i\leq n$}, can be {\em partially observable} (some fluents in $s_i$ are missing because it is unknown whether their value is either positive or negative). %In the extreme, entire states $s_i$ and actions $a_i$ {\small $1\leq i\leq n$}, can be missing. In such scenario solving $\Lambda$ implies determining, not only the \strips\ action model $\mathcal{M}'$, but also the unobserved plan $\pi$, that explains the input observations with the learned \strips\ model.
\item Observations in $\mathcal{T}$ are {\em noiseless}, meaning that if a fluent or an action is observed it is the correct value. 
\end{enumerate}
Figure~\ref{fig:example-plans} shows an example of a learning task $\Lambda=\tup{\mathcal{M},\Psi,\mathcal{T}}$, that corresponds to observing the execution of a four-action plan $\pi=\tup{\small\tt (unstack\ B\ A), (putdown\ B), (pickup\ A), (stack\ A\ B)}$ for inverting a two-block tower. In this example $\mathcal{T}=\langle s_0,${\small\tt (unstack\ B\ A), (putdown\ B), (pickup\ A), (stack\ A\ B)}$,s_4\rangle$ which means that only the first and last states are observed and the three intermediate states $s_1$, $s_2$ and $s_3$ are fully unknown.

>>>>

In this paper we address the $\Lambda=\tup{\mathcal{M},\Psi,\mathcal{T}}$ learning task with the following assumptions:
\begin{enumerate}
\item Each input action scheme $\xi\in\mathcal{M}$ is at least composed of its $head(\xi)$,
\item The initial state $s_0\in\mathcal{T}$ is {\em fully observable}.
\item Intermediate actions $a_i\in\mathcal{T}$ and states $s_i\in\mathcal{T}$ s.t. {\small $1\leq i\leq n$}, can be {\em partially observable} (some fluents in $s_i$ are missing because it is unknown whether their value is either positive or negative). In the extreme, all actions $a_i$, {\small $1\leq i\leq n$}, can be missing (unobserved) provided that the final state $s_n$ is at least, partially observed. Likewise, all states $s_i$, {\small $1\leq i\leq n$}, can be missing (unobserved) provided that at least actions $a_i$, {\small $1\leq i\leq n$}, are partially observed.
 \item Observations in $\mathcal{T}$ are {\em noiseless}, meaning that if a fluent or an action is observed it is the correct value. 
\end{enumerate}
Figure~\ref{fig:example-plans} shows an example of a learning task $\Lambda=\tup{\mathcal{M},\Psi,\mathcal{T}}$, that corresponds to observing the execution of a four-action plan $\pi=\tup{\small\tt (unstack\ B\ A), (putdown\ B), (pickup\ A), (stack\ A\ B)}$ for inverting a two-block tower. In this example $\mathcal{T}=\langle s_0,${\small\tt (unstack\ B\ A), (putdown\ B), (pickup\ A), (stack\ A\ B)}$,s_4\rangle$ which means that only the first and last states are observed and the three intermediate states $s_1$, $s_2$ and $s_3$ are fully unknown.
